---
title: "MSc Statistics Challenge"
subtitle: "Imperial College London"
author: "Presented by Andrew Connell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%/%total%"
  extra_dependencies: ["mathtools", "amsmath", "amssymb"]
  fig_caption: yes
params:
  name1: "Andrew" 
  name2: "Andrew" 
---

```{r xaringanExtra, echo = FALSE}
  xaringanExtra::use_progress_bar(color = "#035AA6", location = "bottom")
```

<!-- edit name1 and name2 in the YAML above -->

# Overview

<br />
--

* The data this year is collected from Spotify.

--

* I asked three people I know to provide me with their libraries (none of them are me).

--

* Your goal is to return a re-classification of what song came from what library.

--

* A song will belong to either $1, 2$ or all $3$ individuals.

--

* There are plenty of resources available online 
--
 (but this problem is slightly different!)
--

* You have until 5pm and I will answer emails throughout the day.

--

* Three prizes: 
--
 $\color{red}{ 1^{\mathrm{st}}: £1500}$, 
--
$\color{blue}{ 2^{\mathrm{nd}}: £600}$, 
--
and $\color{green}{ 3^{\mathrm{rd}}: £400}$.

---

# The Variables

```{r block, dpi = 300, fig.width=10, fig.align='center', include=FALSE}
library(reticulate)
library(fmsb)

spot <- read.csv("spotify.csv")
feature <- spot[, c(4,5,7,9,10,11,12,13,14)]
```

```{r block2, dpi = 300, fig.width=10, fig.align='center', echo = FALSE, warning=FALSE, message=FALSE}
library(knitr)
ltr <- c(4:16)
x <- spot[sample(1:length(spot[,1]), 2), ltr]

kable(x[,1:5]) 
```
<br />
```{r block3, dpi = 300, fig.width=10, fig.align='center', echo = FALSE, warning=FALSE, message=FALSE}
kable(x[,6:9])
```
<br />
```{r block4, dpi = 300, fig.width=10, fig.align='center', echo = FALSE, warning=FALSE, message=FALSE}
kable(x[,10:13])
```

---

# Visualising the Data

```{r Radarchart, dpi = 300, fig.width=10, fig.align='center', eval = TRUE, echo = FALSE}
library(reticulate)
library(fmsb)

spot <- read.csv("spotify.csv")
feature <- spot[, c(4,5,7,9,10,11,12,13,14)]

feature.plot <- function(x){
  # Look at one song
  One_Song <- as.data.frame(feature[x,])
  colnames(One_Song) <- colnames(feature)
  # set boundaries
  mup <- mapply(max, feature); mdown <- mapply(min, feature)
  #
  data <- rbind(mup, mdown, One_Song)
  radarchart(data)
}
# Choose a song and use the function below
feature.plot(1:10)
```

---

# The Website

<br />

The website is available here:       [http://shiny2.ma.ic.ac.uk/users/amc19/MSc/](http://shiny2.ma.ic.ac.uk/users/amc19/MSc/)

--

&nbsp;

- The training data set can be used to rank your scores.

--

&nbsp;

- You will receive a percentage accuracy score.

--

&nbsp;

- We will ask the top three teams to submit their code so we can verify their models.